\cvsection{Work Experience}
\begin{cventries}
  \cvsimpleentry
    {\textbf{Frontend Developer, Kaopiz Software JSC}}
    {Hanoi, Sep. 2025 - Present}
    {
      \begin{cvitems}
        \item {Built and maintained complex data dashboards using ReactJS, Typescript, resulting in a 45\% improvement in page load performance}
        \item {Leveraged Cursor AI agent as the primary coding assistant to accelerate feature development and refactoring, reducing coding and debugging time by 50\%.}
        \item {Designed and optimized a reusable component library with MUI, decreasing development time for new features by approximately 40\%.}
        \item {Implemented advanced state management and server-state caching with Zustand and TanStack Query, enhancing data consistency and application performance.}
        \item {Developed complex dynamic forms with advanced validation using React Hook Form and Zod, enhancing data integrity and reducing submission errors.}
        \item {Collaborated with backend engineers to design and refine APIs, contributing to faster issue resolution and smoother frontend–backend integration.}
      \end{cvitems}
    }
  \cvsimpleentry
    {\textbf{Rookie, NashTech}}
    {Hanoi, Mar. 2025 - May. 2025}
    {
      \begin{cvitems}
        \item {Selected for NashTech’s Rookie training program, an intensive program designed to prepare students for professional software development.}
        \item {Strengthened foundational skills in frontend development, Git workflow, and agile development practices.}
      \end{cvitems}
    }
  \cvsimpleentry
    {\textbf{Frontend Developer Intern, FPT Software}}
    {Hanoi, Sep. 2024 - Mar. 2025}
    {
      \begin{cvitems}
        \item {Developed an extensible JavaScript script using VueJS to create screens, improving pass rates and reducing developed time.}
        \item {Collaborating with BA, and QA teams to enhance user experience.}
        \item {Worked in a cross-functional team, utilizing Git, Azure and Jenkin for version control and deployment.}
      \end{cvitems}
    }
\end{cventries}
