\cvsection{Projects}
\begin{cventries}
  \cvsimpleentry
    {\href{https://github.com/lopica/ai-resume-analyser}{\textbf{AI Resume Analyzer}}}
    {Jul. 2025 - Aug. 2025}
    {
      \begin{cvitems}
        \item {Addressed the need for bilingual (EN/Vi) AI-assisted résumé review from uploaded PDFs within a single SPA experience targeted at production deployment.}
        \item {Built the front end with React, TypeScript, TailwindCSS, React Router; integrated PuterJS with Redux Toolkit Query for AI calls; rendered PDFs with PDF.js.}
        \item {Bolstered assurance with Vitest, Testing Library, and Playwright (unit through E2E) and centralized EN/Vi copy in i18next.}
        \item {Automated delivery with GitHub Actions and Vercel deployments so merged changes ship predictable production builds.}
      \end{cvitems}
    }
    \cvsimpleentry
    {\href{https://github.com/lopica/Nexter}{\textbf{Nexter}}}
    {Jul. 2025 - Aug. 2025}
    {
      \begin{cvitems}
        \item {Delivered a brochure-style luxury real-estate front end as static HTML/SASS (SCSS) aligned with GitHub Pages hosting and repeatable asset builds.}
        \item {Composed semantic sections (hero through listings, gallery, footer CTAs) using responsive Flexbox and Grid for realtor stats, property cards, and breakpoints.}
        \item {Enabled continuous shipping through GitHub Actions so pushes to \texttt{main} rebuild Sass outputs and publish the static bundle to GitHub Pages without manual release steps.}
      \end{cvitems}
    }
\end{cventries}
